CSci487 Penetration Testing Project: AILEE

### 2019-05-06 csci487/project/paper.tex
Editing
Signed-off-by: Misha Turnbull <mishaturnbull@gmail.com>

\tableofcontents

@@

\begin{figure}[htbp]
	\centerline{\includegraphics[scale=2]{exploit-pic}}
	\caption{Running the \textit{exploit} executable}
	\label{fig}
\end{figure}

First, the user enters the number corresponding to the exploit they wish to run. Then, the target IP address is entered, followed by the specific port, and finally the command 'run' must be entered and the exploitation software will attempt to gain access to the target (Fig. 1).

\begin{figure}[htbp]
	\centerline{\includegraphics[scale=2]{loading-new-shell}}
	\caption{Gaining a shell on target machine}
	\label{fig}
\end{figure}

If the exploit is successful, the screen will clear and the words "Loading new shell...." will appear on the screen with increasing dots as the shell loads (Fig. 2).

\begin{figure}[htbp]
	\centerline{\includegraphics[scale=2]{access-granted}}
	\caption{A new shell on an exploited target}
	\label{fig}
\end{figure}

Once the shell loads, the name of the computer exploited will be shown before the /\$ symbol where commands are typed (Fig. 3).

@@

\begin{figure}[htbp]
	\centerline{\includegraphics[scale=1.39]{event3}}
	\caption{The dialogue for event 3}
	\label{fig}
\end{figure}

This is the text for the third event (Fig. 4), which triggers after the user runs the command \textit{pscan} against the first target IP address.

\begin{figure}[hp]
    \centerline{\includegraphics[scale=0.5]{gameflow.png}}
    \caption{The sequence of events in play order}
    \label{fig:gameplay-sequence}
\end{figure}

@@

This is the code for the structure and mechanics of the computer filesystems. 
Similar to Linux, both files and folders have and use discrete permissions, 
marking certain files as executable and readable.  While there are not yet any
provisions for editing/creating files in-game\footnote{The \texttt{gcc} command
creates a file \texttt{a.out}, which promptly throws a segmentation fault.},
the permissions architecture is in place for adding future file-editing
utilities.

@@

\begin{figure}[htbp]
	\centerline{\includegraphics[scale=2]{filesystem-example}}
	\caption{Filesystem navigation}
	\label{fig}
\end{figure}

Directories are colored \textcolor{folder-blue}{\textbf{light blue}}, executables a \textcolor{file-green}{\textbf{light green}}, and regular files are white.  Because of the permissions associated with each file and directory, and the fact that \texttt{File} and \texttt{Directory} objects are implemented as separate classes, there are no special requirements to file/folder names or attributes.  However, due to the difficult implementation of a directory tree, the \textit{ls} command cannot be given a path argument as in real life, and thus can only be used in the current directory.

>>>>

%\tableofcontents

@@

\begin{figure}[h]
	\centerline{\includegraphics[scale=2]{exploit-pic}}
	\caption{Running the \textit{exploit} executable}
	\label{fig:exploit-pic}
\end{figure}

First, the user enters the number corresponding to the exploit they wish to run. Then, the target IP address is entered, followed by the specific port, and finally the command 'run' must be entered and the exploitation software will attempt to gain access to the target (Fig. \ref{fig:exploit-pic})

\begin{figure}[h]
	\centerline{\includegraphics[scale=2]{loading-new-shell}}
	\caption{Gaining a shell on target machine}
	\label{fig:loading}
\end{figure}

If the exploit is successful, the screen will clear and the words "Loading new shell...." will appear on the screen with increasing dots as the shell loads (Fig. \ref{fig:loading})

\begin{figure}[h]
	\centerline{\includegraphics[scale=2]{access-granted}}
	\caption{A new shell on an exploited target}
	\label{fig:access}
\end{figure}

Once the shell loads, the name of the computer exploited will be shown before the /\$ symbol where commands are typed (Fig. \ref{fig:access}).

@@

\begin{figure}[h]
	\centerline{\includegraphics[scale=1.39]{event3}}
	\caption{The dialogue for event 3}
	\label{fig:event3}
\end{figure}

This is the text for the third event (Fig. \ref{fig:event3}), which triggers after the user runs the command \textit{pscan} against the first target IP address.

\begin{figure}[h]
    \centerline{\includegraphics[scale=0.5]{gameflow.png}}
    \caption{The sequence of events in play order}
    \label{fig:gameplay-sequence}
\end{figure}

@@

This is the code for the structure and mechanics of the computer filesystems. 
Similar to Linux, both files and folders have and use discrete permissions, 
marking certain files as readable, writable, and executable.  While there are not yet any
provisions for editing/creating files in-game\footnote{The \texttt{gcc} command
creates a file \texttt{a.out}, which promptly throws a segmentation fault.},
the permissions architecture is in place for adding future file-editing
utilities.

@@

\begin{figure}[htbp]
	\centerline{\includegraphics[scale=2]{filesystem-example}}
	\caption{Filesystem navigation}
	\label{fig:ls-command}
\end{figure}

Directories are colored light blue, executables are light green, and regular files are white.  Because of the permissions associated with each file and directory, and the fact that \texttt{File} and \texttt{Directory} objects are implemented as separate classes, there are no special requirements to file/folder names or attributes.  However, due to the difficult implementation of a directory tree, the \textit{ls} command cannot be given a path argument as in real life, and thus can only be used in the current directory.
